### 2019-02-27 sections/language.tex
reference where evaluation will be discusses in pretask section

\label{sub:pretasks}
The grammar in \cref{fig:task-grammar} specifies the syntactic category of \emph{pretasks}.
Pretasks are tasks that have unevaluated subexpressions.
This means they are considered to be in normal form for the host language, even if their subexpressions are not in normal form.
Each pretask will be discussed in more detail in the following subsections.
We use open symbols ($\Edit, \Enter, \Next, \Xor$) for tasks that require user input, and closed symbols ($\Update, \Then, \Or$) for tasks that can be evaluated without user input.

@@

Typing rules are of the form $\RelationT$, which should be read as \enquote{in environment $\Gamma$ and store typing $\Sigma$, expression $e$ has type $\tau$}.
Typing rules for expressions in the host language are presented in the appendix.
The typing rules for pretasks are given in \cref{fig:typing-rules}.
\fixme{Say someting about why we need beta, and use beta in the acutal typing rule}
\fixme{Alejandro: Is there anything surprising? Say what}
\begin{figure}[h]
  \small
  \begin{gather*}
    \boxed{\RelationT} \Break
    \userule{T-Edit} \Quad
    \userule{T-Enter} \Quad
    \userule{T-Update} \Quad
    \userule{T-Fail} \Break
    \userule{T-Then} \Quad
    \userule{T-Next} \Break
    \userule{T-And} \Quad
    \userule{T-Or} \Quad
    \userule{T-Xor}
  \end{gather*}
  \caption{Typing rules} \label{fig:typing-rules}
\end{figure}

>>>>

\label{sub:pretasks}
The grammar in \cref{fig:task-grammar} specifies the syntactic category of \emph{pretasks}.
Pretasks are tasks that have unevaluated subexpressions with respect to the host language.
Who expressions are evaluated will be discussed in Section~\ref{sec:evaluation}.
Each pretask will be discussed in more detail in the following subsections.
We use open symbols ($\Edit, \Enter, \Next, \Xor$) for tasks that require user input, and closed symbols ($\Update, \Then, \Or$) for tasks that can be evaluated without user input.

@@

Typing rules are of the form $\RelationT$, which should be read as \enquote{in environment $\Gamma$ and store typing $\Sigma$, expression $e$ has type $\tau$}.
Typing rules for expressions in the host language are presented in the appendix.
The typing rules for pretasks are given in \cref{fig:typing-rules}.

\fixme{Say someting about why we need beta, and use beta in the acutal typing rule}
\fixme{Alejandro: Is there anything surprising? Say what}
\begin{figure}[h]
  \small
  \begin{gather*}
    \boxed{\RelationT} \Break
    \userule{T-Edit} \Quad
    \userule{T-Enter} \Quad
    \userule{T-Update} \Quad
    \userule{T-Fail} \Break
    \userule{T-Then} \Quad
    \userule{T-Next} \Break
    \userule{T-And} \Quad
    \userule{T-Or} \Quad
    \userule{T-Xor}
  \end{gather*}
  \caption{Typing rules} \label{fig:typing-rules}
\end{figure}
